---
title: "JA Remote Meeting Analysis"
author: "Shannon Carter"
date: "August 28, 2020"

output: 
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

<style type="text/css">
body { font-size: 16px; line-height:140%: font-family: 'Libre Franklin', sans-serif; color:#333; }
.tocify { font-size: 12px; border:none!important; border-radius:0px!important; }
h2 { font-size:30px; }
#TOC {
  background: url("https://www.januaryadvisors.com/wp-content/uploads/2018/07/ja-logo-horizontal.svg");
  background-size: 80%;
  padding-bottom: 40px !important;
  background-repeat: no-repeat;
  background-position: left bottom;
}
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
background-color: rgb(49,156,244,0.8);
border-color: #319cf4;
}
</style>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
rm(list = ls(all = T))

# load packages
library(tidyverse)
library(highcharter)
library(janitor)
library(here)
library(googlesheets4)
library(config)
library(aws.s3)
library(jastyle)

mytheme <- theme_bw(base_size = 15, base_family = "Franklin Gothic Medium") +
  theme(legend.text = element_text(size = 10),
        legend.title = element_text(size = 11),
        text = element_text(size = 14),     
        axis.title = element_text(size = 12),
        axis.text  = element_text(size = 10, family = "Consolas"),
        panel.grid = element_blank())

# load data
pw <- config::get("aws", file = "config.yml")

Sys.setenv("AWS_ACCESS_KEY_ID" = pw$AWS_ACCESS_KEY_ID,
           "AWS_SECRET_ACCESS_KEY" =  pw$AWS_SECRET_ACCESS_KEY,
           "AWS_DEFAULT_REGION" = pw$AWS_DEFAULT_REGION
)


loadData <- function() {
  df <- s3readRDS(
    bucket = "standupapp",
    object = "standapp-data.rds"
  )
  return(df)
}

df <- loadData()
# df <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lcaht7ezzJxZ5gvh7A5TF9iZkWGAVQ4hJ9yXXH_6dnY/edit#gid=851427512", sheet = "clean-data", na = c("NA", ""))
```

```{r}
hist <- df %>% 
  pivot_longer(cols = Brian:Zach, names_to = "person", values_to = "order") %>%
  filter(date < "2021-02-08") %>% 
  mutate(order = as.numeric(order)) %>% 
  filter(person != "Hala" & person != "Divine" & person != "Zach") %>%
  filter(order < 9) %>% 
  ggplot(aes(x = order)) +
  geom_bar(stat = "count", fill = "dodgerblue") +
  facet_wrap(~person) +
  mytheme +
  scale_x_continuous(breaks = seq(1, 8, 1))
hist

hist2 <- df %>% 
  pivot_longer(cols = Brian:Zach, names_to = "person", values_to = "order") %>% 
  filter(person != "Hala" & person != "Divine" & person != "Zach") %>% 
  filter(order < 9) %>% 
  ggplot(aes(x = order, fill = person)) +
  geom_bar(stat = "count", position = 'dodge') +
  mytheme +
  scale_x_continuous(breaks = seq(1, 8, 1))
hist2
```

```{r}

getMode <- function(x) {
  ux <- na.omit(unique(x) )
 tab <- tabulate(match(x, ux)); ux[tab == max(tab) ]
}

summary <- df %>% 
  summarize(Brian = getMode(Brian)[1],
            Carly = getMode(Carly)[1],
            David = getMode(David)[1],
            Emi = getMode(Emi)[1],
            Jeff = getMode(Jeff)[1],
            Kelsey = getMode(Kelsey)[1],
            Marissa = getMode(Marissa)[1],
            Shannon = getMode(Shannon)[1]) %>% 
  pivot_longer(cols = Brian:Shannon, names_to = "person", values_to = "mode") 

call_on <- df_long %>% 
  filter(!is.na(person_called_on)) %>% 
  group_by(person) %>% 
  arrange(desc(n)) %>% 
  slice_head(n = 1) %>% 
  ungroup() %>% 
  select(person, most_likely_to_call_on = person_called_on)


  
```

```{r}
df_long <- df %>% 
  pivot_longer(cols = Brian:Zach, names_to = "person", values_to = "order") %>%
  #filter(date < "2021-02-08") %>% 
  mutate(order = as.numeric(order)) %>% 
  filter(person != "Hala" & person != "Divine" & person != "Zach") %>%
  filter(order < 9) %>% 
  arrange(date, time, order) %>% 
  group_by(date, time) %>% 
  mutate(person_called_on = lead(person)) %>%
  ungroup() %>% 
  mutate(person_called_on_per_meeting = length(person)) %>% 
  count(person, person_called_on)

d <- df_long %>% 
  filter(!is.na(person_called_on)) %>% 
  filter(n > 1) %>% 
  left_join(denom) %>% 
  mutate(pct = 100*n/denom)

```

```{r}
#Start with wide standapp dataset

getMode <- function(x) {
  ux <- na.omit(unique(x) )
 tab <- tabulate(match(x, ux)); ux[tab == max(tab) ]
}

modes <- df %>% 
  summarize(Brian = getMode(Brian)[1],
            Carly = getMode(Carly)[1],
            David = getMode(David)[1],
            Divine = getMode(Divine)[1],
            Emi = getMode(Emi)[1],
            Hala = getMode(Hala)[1],
            Jeff = getMode(Jeff)[1],
            Kelsey = getMode(Kelsey)[1],
            Marissa = getMode(Marissa)[1],
            Shannon = getMode(Shannon)[1],
            Zach = getMode(Zach)[1]) %>% 
  pivot_longer(cols = Brian:Zach, names_to = "name", values_to = "mode") %>% 
  mutate(mode_pretty = case_when(mode == 1 ~ "1st",
                                 mode == 2 ~ "2nd",
                                 mode == 3 ~ "3rd", 
                                 T ~ paste0(mode, "th")))

#Calculate Number of times each team member was in a meeting with another
columns <- colnames(df)
names <- columns[!columns %in% c("date", "time")]

all_combos <- combn(names, 2) %>% 
  as.data.frame() %>% 
  mutate(
    rowid = row_number()
  ) %>% 
  dplyr::select(rowid, everything()) %>% 
  pivot_longer(V1:V55, names_to = "name1", values_to = "name2") %>% 
  pivot_wider(names_from = "rowid" , values_from = "name2") %>% 
  dplyr::select(-name1) %>% 
  clean_names() %>% 
  mutate(row_id = row_number())

shared_meetings <- df %>% 
  mutate(
    Brian = ifelse(!is.na(Brian), "Brian", NA),
    Carly = ifelse(!is.na(Carly), "Carly", NA),
    David = ifelse(!is.na(David), "David", NA),
    Divine = ifelse(!is.na(Divine), "Divine", NA),
    Emi = ifelse(!is.na(Emi), "Emi", NA),
    Hala = ifelse(!is.na(Hala), "Hala", NA),
    Jeff = ifelse(!is.na(Jeff), "Jeff", NA),
    Kelsey = ifelse(!is.na(Kelsey), "Kelsey", NA),
    Marissa = ifelse(!is.na(Marissa), "Marissa", NA),
    Shannon = ifelse(!is.na(Shannon), "Shannon", NA),
    Zach = ifelse(!is.na(Zach), "Zach", NA),
  ) 

count_shared_meetings <- function(i) {
  select_combo <- filter(all_combos, row_id==i)
  
  count_shared_meetings <- shared_meetings %>% 
    dplyr::select(x1 = select_combo[[1]], x2 = select_combo[[2]]) %>% 
    filter(!is.na(x1) & !is.na(x2)) %>% 
    count(x1, x2)
  return(count_shared_meetings)
}

shared_meeting_count <- all_combos %>%
  group_by(row_id) %>% 
  do(count_shared_meetings(.$row_id)) %>% 
  ungroup() %>% 
  dplyr::select(-row_id)

#Figure out who called on who and divide by number of times they shared a meeting
who_called_on_who <- df %>% 
  pivot_longer(`Brian`:`Zach`, names_to = "name", values_to = "order") %>% 
  mutate(time = factor(time, levels = c("Standup", "Sitdown"))) %>% 
  filter(!is.na(order)) %>% 
  arrange(date, time, order) %>% 
  group_by(date, time) %>% 
  mutate(
    total_n = max(order, na.rm=T),
    called_on = lead(name)
  ) %>% 
  ungroup() %>% 
  filter(!is.na(called_on)) %>% 
  count(name, called_on)

#Figure out who called on who and divide by number of times they shared a meeting
who_called_on_by <- df %>% 
  pivot_longer(`Brian`:`Zach`, names_to = "name", values_to = "order") %>% 
  mutate(time = factor(time, levels = c("Standup", "Sitdown"))) %>% 
  filter(!is.na(order)) %>% 
  arrange(date, time, order) %>% 
  group_by(date, time) %>% 
  mutate(
    total_n = max(order, na.rm=T),
    called_on_by = lag(name)
  ) %>% 
  ungroup() %>% 
  filter(!is.na(called_on_by)) %>% 
  count(name, called_on_by)


who_rates <- who_called_on_who %>% 
  left_join(., shared_meeting_count, by=c("name" = "x1", "called_on" = "x2")) %>% 
  left_join(., shared_meeting_count, by=c("name" = "x2", "called_on" = "x1")) %>% 
  mutate(
    total_shared_meetings = ifelse(is.na(n.y), n, n.y),
    called_on_adj = n.x/total_shared_meetings
  ) %>% 
  dplyr::select(name, called_on, n = n.x, total_shared_meetings, called_on_adj)

who_rates_by <- who_called_on_by %>% 
  left_join(., shared_meeting_count, by=c("name" = "x1", "called_on_by" = "x2")) %>% 
  left_join(., shared_meeting_count, by=c("name" = "x2", "called_on_by" = "x1")) %>% 
  mutate(
    total_shared_meetings = ifelse(is.na(n.y), n, n.y),
    called_on_adj = n.x/total_shared_meetings
  ) %>% 
  dplyr::select(name, called_on_by, n = n.x, total_shared_meetings, called_on_adj)

called_on_most_by <- who_rates_by %>% 
  filter(n > 5) %>% 
  group_by(name) %>% 
  mutate(called_on_adj = round(100 * called_on_adj, 1)) %>% 
  arrange(desc(called_on_adj)) %>% 
  slice_head(n = 1) %>% 
  select(name, called_on_by_most = called_on_by, called_on_by_x_times = n, called_on_by_x_pct = called_on_adj)

heatmap <- who_rates %>% 
        filter(name != "Hala" & name != "Divine" & name != "Zach") %>% 
        filter(called_on != "Hala" & called_on != "Divine" & called_on != "Zach") %>% 
        filter(!is.na(total_shared_meetings)) %>% 
        ggplot(aes(x=called_on, y=name, fill=called_on_adj)) + 
        geom_tile(color = "white") +
        scale_fill_gradient2(low = "#5c9ad2", high = "#f59035",
                             midpoint = 0.14, limit = c(0, 0.4)) +
        labs(title = "Who calls on whom?") +
        theme_bw() +
        labs(y = "Person", x = "Calls On", fill = "frequency") +
        theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(),
              text = element_text(size = 14, family = "Roboto"),
              legend.position = "bottom",
              #axis.text.x = element_text(angle = 45, hjust = 1),
              plot.title.position = "plot",
              plot.title = element_text(face="bold")
              )
ggsave("heatmap.jpg", width = 8.5, height = 5.5, units = "in", dpi = 600)

stats <- who_rates %>% 
  filter(n > 5) %>% 
  group_by(name) %>% 
  mutate(called_on_adj = round(100 * called_on_adj, 1)) %>% 
  arrange(desc(called_on_adj)) %>% 
  slice_head(n = 1) %>% 
  select(name, calls_on_most = called_on, called_on_x_times = n, called_on_x_pct = called_on_adj) %>% 
  left_join(modes) %>% 
  left_join(called_on_most_by)
```


```{r}
calendar <- df %>% 
  filter(date != "2021-03-11" & date != "2021-03-12") %>% 
  #tail(50) %>% 
  select(-c(Divine, Hala, Zach)) %>% 
  rename(B = Brian, C = Carly, D = David, E = Emi, J = Jeff, K = Kelsey, M = Marissa, S = Shannon) %>% 
  mutate(index = 1:length(date),
         date_index = as.numeric(paste0(year(date), month(date))),
         index2 = case_when(date_index == 20204 ~ 1,
                            date_index == 20205 ~ 2,
                            date_index == 20206 ~ 3,
                            date_index == 20207 ~ 4,
                            date_index == 20208 ~ 5,
                            date_index == 20209 ~ 6,
                            date_index == 202010 ~ 7,
                            date_index == 202011 ~ 8,
                            date_index == 202012 ~ 9,
                            date_index == 20211 ~ 10,
                            date_index == 20212 ~ 11,
                            date_index == 20213 ~ 12)) %>% 
  pivot_longer(B:S) %>% 
  mutate(value = factor(value, levels = c("1", "2", "3", "4", "5", "6", "7", "8"), ordered = T)) %>% 
  ggplot(aes(x = index, y = name, fill = value)) +
  geom_tile(color = "white", size = 0) + 
  facet_wrap(~index2, scales = "free", nrow = 1) + 
  scale_fill_manual(values = c("#ff0000", "#f59035", "#ffff00", "#149414", "#5c9ad2", "#2b5bb0", "#663399", "#ff69b4")) + 
  theme_void() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 6, family = "Roboto"),
        panel.spacing = unit(0, "lines")) + 
  coord_flip()
calendar
ggsave("tile_plot.jpg", width = 13, height = 8, units = "in", dpi = 600)
```


```{r}

meetings_since <- length(df$date[as.numeric(rownames(df)) > 432])
freq_missing <- df %>% 
  select(-c("Divine", "Hala", "Zach")) %>% 
  pivot_longer(`Brian`:`Shannon`, names_to = "name", values_to = "order") %>% 
  mutate(time = factor(time, levels = c("Standup", "Sitdown"))) %>% 
  filter(!is.na(order)) %>% 
  group_by(name) %>% 
  summarize(number_attended = length(name),
            number_meetings = case_when(name == "Brian" ~ 432 + meetings_since,
                                        name == "Carly" ~ 324 + meetings_since,
                                        name == "David" ~ 432 + meetings_since,
                                        name == "Emi" ~ 188 + meetings_since,
                                        name == "Jeff" ~ 432 + meetings_since,
                                        name == "Kelsey" ~ 432 + meetings_since,
                                        name == "Marissa" ~ 173 + meetings_since,
                                        name == "Shannon" ~ 432 + meetings_since)) %>%
  mutate(freq_missing = round(100 - (number_attended/number_meetings)*100, 1)) %>% 
  distinct() %>% 
  select(name, freq_missing)

freq_first_last <- df %>% 
  select(-c("Divine", "Hala", "Zach")) %>% 
  pivot_longer(`Brian`:`Shannon`, names_to = "name", values_to = "order") %>% 
  mutate(time = factor(time, levels = c("Standup", "Sitdown"))) %>% 
  filter(!is.na(order)) %>% 
  group_by(date, time) %>% 
  mutate(last_position = max(order)) %>% 
  ungroup() %>% 
  group_by(name) %>% 
  summarize(number_meetings = length(order),
            number_last = length(order[order == last_position]),
            number_first = length(order[order == 1])) %>%
  mutate(freq_last = round((number_last/number_meetings)*100, 2),
         freq_first = round((number_first/number_meetings)*100, 2)) %>% 
  left_join(freq_missing)

make_bar_chart <- function(.data, .x_var, .y_var, .x_axis_name, .title) {
  x_var <- enquo(.x_var)
  y_var <- enquo(.y_var)
  
  ggplot(freq_first_last, aes(x = !!x_var, y = reorder(!!y_var, !!x_var))) +
    geom_bar(stat = "identity", fill = "#5c9ad2", size = 2) +
    geom_text(aes(label = paste0(round(!!x_var), "%")), hjust=1, family="Roboto", fontface="bold", color = "white") +
    labs(
      title = .title,
      x = .x_axis_name,
      y = NULL) +
    theme_bw()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.ticks = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12, family = "Roboto"),
          text = element_text(size = 12, family = "Roboto"),
          plot.title.position = "plot",
          plot.title = element_text(face="bold", size=16)
          )
}

first <- make_bar_chart(freq_first_last, freq_first, name, "% of meetings first", "Who goes first?")
last <- make_bar_chart(freq_first_last, freq_last, name, "% of meetings last",  "Who goes last?")
missing <- make_bar_chart(freq_first_last, freq_missing, name, "% of meetings missed",  "Who skips?")
      
grid.arrange(grobs=list(first, last), ncol=2)
   
```
```{r}
csa <- df %>% 
  select(date, time, Carly, Shannon) %>% 
  mutate(c_s = Shannon - Carly) %>% 
  filter(!is.na(c_s)) %>% 
  filter(date > "2020-07-01")
```

